```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      fig.width = 10, fig.height = 6, out.width = "100%")

# Load required libraries
library(tidyverse)
library(stringr)
library(gridExtra)
library(car)       # For statistical testing
library(broom)     # For tidy model outputs
library(kableExtra) # For nice tables
library(viridis)   # For color palettes
```

# Forecasting Model-Prompt Analysis

This analysis examines how different prompting strategies affect the forecasting accuracy of large language models, measured using Brier scores.

## 1. Data Loading and Inspection

First, let's load the necessary datasets:

```{r load_data}
# Load datasets
questions_sample <- read_csv("datasets/question_sample_2024-12-08.csv")
model_questions <- read_csv("datasets/questions_models_2024-12-08.csv")
sonnet <- read_csv("data/sonnet.csv")

# Quick inspection of datasets
cat("Questions sample dimensions:", dim(questions_sample), "\n")
cat("Model questions dimensions:", dim(model_questions), "\n")
cat("Sonnet responses dimensions:", dim(sonnet), "\n")

# Examine sample structures
head(questions_sample, 3) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

head(model_questions, 3) %>% 
  select(id, question_id, prompt_id, model_name) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

head(sonnet, 3) %>% 
  select(recordId, modelInput_messages_content_text, modelOutput_content_text) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```


## 2. Create Prompt Name Mapping

Let's create a mapping of prompt IDs to their descriptive names:

```{r prompt_mapping}
# Create prompt name mapping
prompt_names <- tibble(
  prompt_id = 1:38,
  prompt_name = c(
    "Control",
    "Chain of Thought",
    "Self-Consistency",
    "Few-Shot",
    "Step-Back",
    "High Personal Stakes",
    "Echo",
    "Structure",
    "Emotional Prompt",
    "Re-Reading",
    "Uncertainty Quantification",
    "Superforecasting Persona",
    "Abstention",
    "Counterfactual Reasoning",
    "Analogical Reasoning",
    "Hypothetical Scenario Analysis",
    "Scoring Rule",
    "Premortem",
    "Base Rate First",
    "Time Decomposition",
    "Metacognition",
    "Anti-Biasing (Anchoring)",
    "Anti-Biasing (Round Numbers)",
    "Anti-Biasing (Overconfidence)",
    "Frequency-Based Reasoning",
    "Propose-Evaluate-Select",
    "Bayesian Reasoning",
    "Multiple Reference Classes",
    "Fermi Estimate",
    "Self-Critique",
    "Tipping",
    "Question Paraphrasing",
    "Simulated Dialogue",
    "Simulated Debate",
    "Pros & Cons",
    "Event Decomposition",
    "Deep Breath",
    "Explicit Uncertainty Sources"
  )
)

prompt_names %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```


## 3. Process Sonnet Responses

Now let's extract the forecast values from the model responses:

```{r extract_forecasts}
# Function to extract probabilistic forecasts
extract_forecast <- function(text) {
  if (is.na(text)) return(NA)
  
  # Find patterns like "Forecast: 52%" or "Forecast: 48.5%"
  matches <- str_match(text, "Forecast:[\\s\\*]*(\\d*\\.?\\d+)%")
  
  if (!is.na(matches[1,2])) {
    # Convert to probability (0-1 scale)
    return(as.numeric(matches[1,2]) / 100)
  } else {
    return(NA)
  }
}

# Test the function with a sample response
sample_text <- "Forecast: 52%\n\nI'm providing a slight edge towards higher temperatures"
cat("Extracted forecast:", extract_forecast(sample_text), "\n")

# Apply to sonnet responses
sonnet_with_forecasts <- sonnet %>%
  mutate(forecast = map_dbl(modelOutput_content_text, extract_forecast))

# Check extraction success rate
forecast_success <- sum(!is.na(sonnet_with_forecasts$forecast))
cat("Successfully extracted", forecast_success, "forecasts out of", 
    nrow(sonnet_with_forecasts), "responses (", 
    round(forecast_success/nrow(sonnet_with_forecasts)*100, 1), "%)\n")

# Show sample of extracted forecasts
sonnet_with_forecasts %>%
  select(recordId, forecast) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```



## 4. Match with Model Questions

Let's directly use the recordId to match with model_questions:

```{r match_ids}
# Extract numeric part from recordId (after "request-")
sonnet_with_ids <- sonnet_with_forecasts %>%
  mutate(
    record_num = as.numeric(str_extract(recordId, "\\d+")) - 1  # Subtract 1 to account for 0-indexing
  )

# Verify extraction with a few examples
sonnet_with_ids %>%
  select(recordId, record_num) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Map to model_questions to get question_id and prompt_id
sonnet_mapped <- sonnet_with_ids %>%
  left_join(
    model_questions %>% 
      select(id, question_id, prompt_id),
    by = c("record_num" = "id")
  )

# Check mapping success
mapping_success <- sum(!is.na(sonnet_mapped$question_id))
cat("Successfully mapped", mapping_success, "responses to question IDs (", 
    round(mapping_success/nrow(sonnet_mapped)*100, 1), "%)\n")

# Examine the distribution of prompt IDs
prompt_distribution <- sonnet_mapped %>%
  count(prompt_id) %>%
  arrange(desc(n))

prompt_distribution %>%
  head(10) %>%
  kable(caption = "Distribution of responses by prompt ID") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Final processing - clean up and add model name
sonnet_processed <- sonnet_mapped %>%
  mutate(model = "sonnet") %>%
  select(
    model, recordId, question_id, prompt_id, forecast, 
    input_text = modelInput_messages_content_text,
    output_text = modelOutput_content_text
  )

# Show sample of processed results
sonnet_processed %>%
  select(recordId, question_id, prompt_id, forecast) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```

## 5. Calculate Brier Scores

Now let's merge with the actual outcomes and calculate Brier scores:

```{r brier_scores}
# Merge with actual outcomes
sonnet_with_outcomes <- sonnet_processed %>%
  inner_join(
    questions_sample %>% select(question_id, resolved_to),
    by = "question_id"
  )

# Calculate Brier scores
sonnet_with_brier <- sonnet_with_outcomes %>%
  mutate(brier_score = (forecast - resolved_to)^2)

# Check how many valid scores we have
cat("Valid responses with Brier scores:", nrow(sonnet_with_brier), "\n")

# Show sample of Brier scores
sonnet_with_brier %>%
  select(recordId, question_id, prompt_id, forecast, resolved_to, brier_score) %>%
  head(10) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Overall Brier score
overall_brier <- mean(sonnet_with_brier$brier_score, na.rm = TRUE)
cat("Overall average Brier score:", round(overall_brier, 4), "\n")
```


## 6. Analyze Prompt Performance

Now let's analyze performance by prompt type:

```{r prompt_performance}
# Add prompt names
sonnet_with_names <- sonnet_with_brier %>%
  left_join(prompt_names, by = "prompt_id")

# Aggregate by prompt
prompt_performance <- sonnet_with_names %>%
  group_by(prompt_id, prompt_name) %>%
  summarize(
    mean_brier = mean(brier_score, na.rm = TRUE),
    sd_brier = sd(brier_score, na.rm = TRUE),
    count = n(),
    mean_forecast = mean(forecast, na.rm = TRUE),
    sd_forecast = sd(forecast, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(mean_brier)

# Show prompt performance
prompt_performance %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Get control prompt score
control_score <- prompt_performance %>%
  filter(prompt_id == 1) %>%
  pull(mean_brier)

# Calculate improvement over baseline
prompt_performance <- prompt_performance %>%
  mutate(
    improvement = control_score - mean_brier,
    percent_improvement = (improvement / control_score) * 100
  ) %>%
  arrange(desc(percent_improvement))

# Show improvement over baseline
prompt_performance %>%
  select(prompt_id, prompt_name, mean_brier, improvement, percent_improvement, count) %>%
  # filter(abs(percent_improvement) > 0.1) %>% # Filter for meaningful differences
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```

## 7. Check Prompt Consistency

Let's examine how consistently each prompt performs across different questions:

```{r prompt_consistency}
# Calculate consistency across questions
prompt_by_question <- sonnet_with_brier %>%
  group_by(prompt_id, question_id) %>%
  summarize(
    question_brier = mean(brier_score, na.rm = TRUE),
    .groups = "drop"
  )

prompt_consistency <- prompt_by_question %>%
  group_by(prompt_id) %>%
  summarize(
    question_count = n(),
    question_std = sd(question_brier, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  left_join(prompt_names, by = "prompt_id") %>%
  arrange(question_std)

# Show prompt consistency
prompt_consistency %>%
  filter(question_count >= 5) %>%  # Only include prompts with enough questions
  select(prompt_id, prompt_name, question_count, question_std) %>%
  kable(caption = "Prompt consistency across questions (lower std dev = more consistent)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```

## 8. Visualize Prompt Performance

Let's create some visualizations of the results:

```{r visualize_prompts, fig.height=8}
# Ensure we have at least 5 data points for each prompt
reliable_prompts <- prompt_performance %>%
  filter(count >= 10)  # Only include prompts with sufficient data

# Top 10 prompts by performance
reliable_prompts %>%
  top_n(10, percent_improvement) %>%
  mutate(prompt_name = reorder(prompt_name, percent_improvement)) %>%
  ggplot(aes(x = percent_improvement, y = prompt_name, fill = percent_improvement)) +
  geom_col() +
  scale_fill_viridis() +
  labs(
    title = "Top 10 Prompts by Improvement over Control",
    subtitle = "Claude 3.5 Sonnet Model",
    x = "Percent Improvement (%)",
    y = "Prompt Type",
    fill = "% Improvement"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +
  geom_text(aes(label = sprintf("n=%d", count)), hjust = -0.1)

# Distribution of Brier scores by prompt type
top_prompts <- reliable_prompts %>%
  top_n(5, percent_improvement) %>%
  pull(prompt_id)

bottom_prompts <- reliable_prompts %>%
  top_n(5, -percent_improvement) %>%
  pull(prompt_id)

comparison_prompts <- c(1, top_prompts, bottom_prompts) %>% unique()

sonnet_with_names %>%
  filter(prompt_id %in% comparison_prompts) %>%
  mutate(prompt_type = case_when(
    prompt_id == 1 ~ "Control",
    prompt_id %in% top_prompts ~ "Top Performers",
    prompt_id %in% bottom_prompts ~ "Bottom Performers"
  )) %>%
  ggplot(aes(x = reorder(prompt_name, -brier_score, mean), y = brier_score, fill = prompt_type)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Set1") +
  labs(
    title = "Distribution of Brier Scores by Prompt Type",
    subtitle = "Comparing top and bottom performers against control",
    x = "Prompt Type",
    y = "Brier Score (lower is better)",
    fill = "Prompt Category"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Visualize sample counts by prompt type
prompt_performance %>%
  ggplot(aes(x = reorder(prompt_name, -count), y = count, fill = prompt_id == 1)) +
  geom_col() +
  scale_fill_manual(values = c("#1F77B4", "#FF7F0E"), 
                    labels = c("Experimental", "Control")) +
  labs(
    title = "Sample Counts by Prompt Type",
    x = "Prompt Type",
    y = "Number of Samples",
    fill = "Prompt Type"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8),
        legend.position = "top")
```

## 9. Statistical Testing

Let's test if the differences between prompts are statistically significant:

```{r statistical_testing}
# Only test prompts with sufficient data
testable_prompts <- prompt_performance %>%
  filter(count >= 10) %>%
  arrange(desc(percent_improvement))

# Get best prompt with sufficient data
if (nrow(testable_prompts) > 0) {
  best_prompt_id <- testable_prompts$prompt_id[1]
  best_prompt_name <- testable_prompts$prompt_name[1]
  
  # T-test comparing best prompt to control
  best_data <- sonnet_with_brier %>% filter(prompt_id == best_prompt_id)
  control_data <- sonnet_with_brier %>% filter(prompt_id == 1)
  
  if (nrow(best_data) >= 5 && nrow(control_data) >= 5) {
    t_test_result <- t.test(best_data$brier_score, control_data$brier_score, var.equal = FALSE)
    
    cat("T-test comparing best prompt (", best_prompt_name, ") to control:\n")
    cat("t =", round(t_test_result$statistic, 3), ", p-value =", round(t_test_result$p.value, 3), "\n")
    cat("Mean Brier score (best prompt):", round(mean(best_data$brier_score, na.rm = TRUE), 4), "\n")
    cat("Mean Brier score (control):", round(mean(control_data$brier_score, na.rm = TRUE), 4), "\n")
  } else {
    cat("Not enough data for best prompt to perform statistical test\n")
  }
} else {
  cat("No prompts with sufficient data for statistical testing\n")
}

# ANOVA for prompt effect
# Only include prompts with at least 10 observations
anova_data <- sonnet_with_brier %>%
  inner_join(
    prompt_performance %>% filter(count >= 10) %>% select(prompt_id),
    by = "prompt_id"
  )

if (n_distinct(anova_data$prompt_id) > 2) {
  prompt_anova <- aov(brier_score ~ as.factor(prompt_id), data = anova_data)
  anova_summary <- summary(prompt_anova)
  
  cat("\nANOVA for Overall Prompt Effect:\n")
  print(anova_summary)
  
  # Effect size (partial eta squared)
  anova_table <- anova(prompt_anova)
  eta_squared <- anova_table$`Sum Sq`[1] / sum(anova_table$`Sum Sq`)
  
  cat("Effect size (partial eta squared):", round(eta_squared, 4), "\n")
  
  # Pairwise comparisons with control
  if (1 %in% unique(anova_data$prompt_id)) {
    # Only compare experimental prompts to control
    experimental_prompts <- setdiff(unique(anova_data$prompt_id), 1)
    
    cat("\nPairwise comparisons with control (Dunnett's test):\n")
    for (p_id in experimental_prompts) {
      prompt_data <- anova_data %>% filter(prompt_id == p_id)
      control_data <- anova_data %>% filter(prompt_id == 1)
      
      prompt_mean <- mean(prompt_data$brier_score, na.rm = TRUE)
      control_mean <- mean(control_data$brier_score, na.rm = TRUE)
      difference <- control_mean - prompt_mean
      percent_diff <- (difference / control_mean) * 100
      
      t_result <- t.test(prompt_data$brier_score, control_data$brier_score, var.equal = FALSE)
      
      p_name <- prompt_names %>% filter(prompt_id == p_id) %>% pull(prompt_name)
      
      cat(sprintf("Prompt %d (%s): diff = %.4f (%.1f%%), p = %.3f, n = %d\n", 
                  p_id, p_name, difference, percent_diff, t_result$p.value, nrow(prompt_data)))
    }
  }
}
```

## 10. Extend Analysis to Other Models

Now let's extend this analysis to the other models:

```{r other_models}
# Function to process model data
process_model <- function(model_name, model_data) {
  
  cat("\nProcessing", model_name, "model with", nrow(model_data), "responses\n")
  
  # Extract forecasts and match with model_questions
  model_processed <- model_data %>%
    mutate(
      forecast = map_dbl(modelOutput_content_text, extract_forecast),
      record_num = as.numeric(str_extract(recordId, "\\d+")) - 1
    ) %>%
    left_join(
      model_questions %>% select(id, question_id, prompt_id),
      by = c("record_num" = "id")
    ) %>%
    mutate(model = model_name) %>%
    select(
      model, recordId, question_id, prompt_id, forecast,
      input_text = modelInput_messages_content_text,
      output_text = modelOutput_content_text
    )
  
  # Merge with outcomes and calculate Brier scores
  model_with_brier <- model_processed %>%
    inner_join(
      questions_sample %>% select(question_id, resolved_to),
      by = "question_id"
    ) %>%
    mutate(brier_score = (forecast - resolved_to)^2)
  
  # Report statistics
  valid_rows <- nrow(model_with_brier)
  mean_brier <- mean(model_with_brier$brier_score, na.rm = TRUE)
  
  cat("Valid rows with Brier scores:", valid_rows, "\n")
  cat("Overall Brier score:", round(mean_brier, 4), "\n")
  
  return(model_with_brier)
}

# Process all models
model_list <- c("haiku", "llama", "gpt4o")
all_models_data <- list()

haiku <- read_csv("data/haiku.csv") 
all_models_data[["haiku"]] <- process_model("haiku", haiku)

llama <- read_csv("data/llama.csv") %>%
  mutate(
    modelOutput_content_text = modelOutput_generation,
    modelInput_messages_content_text = modelInput_prompt,
  )
all_models_data[["llama"]] <- process_model("llama", llama)


gpt4o <- read_csv("data/gpt4o.csv") %>%
  mutate(
    modelOutput_content_text = choice_message_content,
    modelInput_messages_content_text = choice_message_content,
    recordId = custom_id
  )
all_models_data[["gpt4o"]] <- process_model("gpt4o", gpt4o)


# Add sonnet data to the list
all_models_data[["sonnet"]] <- sonnet_with_brier

# Combine all model data
combined_data <- bind_rows(all_models_data)

# Check distribution of data by model
model_counts <- combined_data %>%
  group_by(model) %>%
  summarize(
    count = n(),
    mean_brier = mean(brier_score, na.rm = TRUE),
    .groups = "drop"
  )

model_counts %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)
```


## 11. Cross-Model Analysis

Now let's compare performance across models:

```{r cross_model}
# Add prompt names to combined data

combined_data_with_names <- combined_data %>%
  left_join(prompt_names, by = "prompt_id")

# Calculate prompt performance by model
prompt_by_model <- combined_data_with_names %>%
  group_by(model, prompt_id, prompt_name) %>%
  summarize(
    mean_brier = mean(brier_score, na.rm = TRUE),
    sd_brier = sd(brier_score, na.rm = TRUE),
    count = n(),
    .groups = "drop"
  )

# Get control scores for each model
control_by_model <- prompt_by_model %>%
  filter(prompt_id == 1) %>%
  select(model, control_score = mean_brier)

# Calculate improvement over control for each model
prompt_improvement <- prompt_by_model %>%
  left_join(control_by_model, by = "model") %>%
  mutate(
    improvement = control_score - mean_brier,
    percent_improvement = (improvement / control_score) * 100
  )

# Show top 5 prompts for each model
top_prompts_by_model <- prompt_improvement %>%
  group_by(model) %>%
  top_n(5, percent_improvement) %>%
  arrange(model, desc(percent_improvement))

top_prompts_by_model %>%
  select(model, prompt_id, prompt_name, mean_brier, percent_improvement) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Create a wide format table of Brier scores by prompt and model
prompt_performance_wide <- prompt_by_model %>%
  select(model, prompt_id, prompt_name, mean_brier) %>%
  pivot_wider(
    names_from = model,
    values_from = mean_brier
  ) %>%
  rowwise() %>%
  mutate(
    average = mean(c_across(c(gpt4o, haiku, sonnet, llama)), na.rm = TRUE),
    std_dev = sd(c_across(c(gpt4o, haiku, sonnet, llama)), na.rm = TRUE)
  ) %>%
  arrange(average) %>%
  ungroup()

# Show top 10 prompts by average performance
prompt_performance_wide %>%
  top_n(10, -average) %>%
  select(prompt_id, prompt_name, average, std_dev, everything()) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

```

## 12. Visualize Cross-Model Comparisons

Let's create visualizations of cross-model performance:

```{r cross_model_viz}
# Overall model comparison
model_counts %>%
  ggplot(aes(x = reorder(model, mean_brier), y = mean_brier, fill = model)) +
  geom_col() +
  geom_text(aes(label = round(mean_brier, 4)), vjust = -0.5) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Overall Model Performance Comparison",
    x = "Model",
    y = "Mean Brier Score (lower is better)",
    fill = "Model"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

# Prompt performance across models (top 5 by average)
top_prompts <- prompt_performance_wide %>%
  top_n(5, -average) %>%
  pull(prompt_id)

prompt_improvement %>%
  filter(prompt_id %in% c(1, top_prompts)) %>%  # Include control + top prompts
  mutate(
    prompt_name = factor(prompt_name, 
                         levels = c("Control", prompt_names$prompt_name[prompt_names$prompt_id %in% top_prompts])),
    model = factor(model)
  ) %>%
  ggplot(aes(x = prompt_name, y = mean_brier, fill = model)) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Top 5 Prompts Performance Across Models",
    subtitle = "Compared to Control Prompt",
    x = "Prompt Type",
    y = "Mean Brier Score (lower is better)",
    fill = "Model"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Correlation of prompt effects between models
prompt_correlation <- prompt_by_model %>%
  select(model, prompt_id, mean_brier) %>%
  pivot_wider(
    names_from = model,
    values_from = mean_brier
  ) %>%
  select(-prompt_id) %>%
  cor(use = "pairwise.complete.obs")

# Visualization of correlation matrix
prompt_correlation %>%
  as.data.frame() %>%
  rownames_to_column("model1") %>%
  pivot_longer(
    cols = -model1,
    names_to = "model2",
    values_to = "correlation"
  ) %>%
  ggplot(aes(x = model1, y = model2, fill = correlation)) +
  geom_tile() +
  geom_text(aes(label = round(correlation, 2)), color = "white") +
  scale_fill_viridis() +
  labs(
    title = "Correlation of Prompt Effects Between Models",
    x = "Model",
    y = "Model",
    fill = "Correlation"
  ) +
  theme_minimal()
```

## 11. Most Universal Prompts

Finally, let's identify the prompts that work well across all models:

```{r universal_prompts}
# Calculate average rank for each prompt across models
prompt_ranks <- prompt_by_model %>%
  group_by(model) %>%
  mutate(rank = rank(mean_brier)) %>%
  group_by(prompt_id, prompt_name) %>%
  summarize(
    avg_rank = mean(rank, na.rm = TRUE),
    std_rank = sd(rank, na.rm = TRUE),
    avg_brier = mean(mean_brier, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(avg_rank)

# Show top universal prompts
prompt_ranks %>%
  top_n(10, -avg_rank) %>%
  select(prompt_id, prompt_name, avg_rank, std_rank, avg_brier) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Show most consistent prompts (lowest standard deviation in rank)
prompt_ranks %>%
  top_n(10, -std_rank) %>%
  arrange(std_rank) %>%
  select(prompt_id, prompt_name, avg_rank, std_rank, avg_brier) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 11)

# Visualize universal prompts
prompt_ranks %>%
  top_n(10, -avg_rank) %>%
  mutate(prompt_name = reorder(prompt_name, -avg_rank)) %>%
  ggplot(aes(x = prompt_name, y = avg_rank, fill = avg_brier)) +
  geom_col() +
  scale_fill_viridis() +
  labs(
    title = "Most Universal Prompts Across All Models",
    subtitle = "Based on average rank (lower is better)",
    x = "Prompt Type",
    y = "Average Rank",
    fill = "Avg Brier Score"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



# Visualize universal prompts
prompt_ranks %>%
  top_n(10, avg_rank) %>%
  mutate(prompt_name = reorder(prompt_name, -avg_rank)) %>%
  ggplot(aes(x = prompt_name, y = avg_rank, fill = avg_brier)) +
  geom_col() +
  scale_fill_viridis() +
  labs(
    title = "Worst Prompts Across All Models",
    subtitle = "Based on average rank (lower is better)",
    x = "Prompt Type",
    y = "Average Rank",
    fill = "Avg Brier Score"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## 12. Conclusions

Based on our analysis, we can draw the following conclusions:

1. The best performing prompts for Sonnet were: `r if(exists("prompt_performance")) {paste(prompt_performance %>% top_n(3, percent_improvement) %>% pull(prompt_name), collapse=", ")}`

2. The worst performing prompts were: `r if(exists("prompt_performance")) {paste(prompt_performance %>% top_n(3, -percent_improvement) %>% pull(prompt_name), collapse=", ")}`

3. The prompt with the most consistent performance was: `r if(exists("prompt_performance")) {paste(prompt_performance %>% arrange(sd_brier) %>% slice(1) %>% pull(prompt_name))}`

4. Statistical significance: `r if(exists("t_test_result")) {if(t_test_result$p.value < 0.05) {"The difference between the best prompt and control is statistically significant."} else {"The difference between the best prompt and control is not statistically significant."}}`

5. `r if(exists("prompt_ranks")) {paste0("Across all models, the most universal prompt was: ", prompt_ranks %>% slice(1) %>% pull(prompt_name))}`

This analysis provides insights into how different prompting strategies affect the forecasting accuracy of large language models, with important implications for building more accurate forecasting systems.